Legacy Data Confounds Modern Genomics Studies

### 2018-05-12 Draft3.tex
Updated Figure 3, minor edits introduction

The last 5 years have seen an increase in the number of individuals genotyped through private companies or medical research cohorts. 
Larger sample sizes allow researchers to identify finer resolution statistically significant differences between groups of individuals. 
Mutations associated to a disease can be identified by comparing the genomes of healthy individuals to those afflicted by a disease. 
The mutations commonly found in patients and rarely in controls might be associated to the disease in question.
However, demonstrating that these mutations are biologically relevant can be difficult.
Especially with the increasing size of cohorts, spurious associations are increasingly becoming an issue. 
For this reason, careful consideration must be taken when including individuals from different ancestral origins in these association studies.
Benign mutations at high frequencies in one populations might be exceedingly rare in another population.
Therefore, population wide differences in mutations must be included as covariates to avoid spurious associations.

\sgcomment{This intro paragraph is much too vague -- it reads like general thoughts about genetics at large. We need to be much more concise. I would start with something like:}

>>>>

%The last 5 years have seen an increase in the number of individuals genotyped through private companies or medical research cohorts. 
%Larger sample sizes allow researchers to identify finer resolution statistically significant differences between groups of individuals. 
%Mutations associated to a disease can be identified by comparing the genomes of healthy individuals to those afflicted by a disease. 
%The mutations commonly found in patients and rarely in controls might be associated to the disease in question.
%However, demonstrating that these mutations are biologically relevant can be difficult.
%Especially with the increasing size of cohorts, spurious associations are increasingly becoming an issue. 
%For this reason, careful consideration must be taken when including individuals from different ancestral origins in these association studies.
%Benign mutations at high frequencies in one populations might be exceedingly rare in another population.
%Therefore, population wide differences in mutations must be included as covariates to avoid spurious associations.

%\sgcomment{This intro paragraph is much too vague -- it reads like general thoughts about genetics at large. We need to be much more concise. I would start with something like:}
